Selecting and ranking interesting pairs of cyclic temporal granularities

### 2021-01-12 paper/main.Rmd
adding vary_x raw results

## Distribution of wpd under $D_{null}$

@@

### dist

wpd is computed for different normal and non-normal distributions to see how the underlying distribution has a role to play in the value of wpd. Since we are concerned with detecting the differences in distributions, it would be ideal if wpd has minimal dependency on the type, location and scale of the  underlying distribution. To that end, some pre-processing of the data is preferred to bring it to the same scale, location and type.
The Normal Score Transform or NQT has been applied in various fields of geo-statistics in order to make the mostly asymmetrical distributed real world measured variables more
treatable and normal-like.

@@

**Objective:** 1. Study the behavior of wpd under different initial distributions for different $nx$ and $nfacet$.
<!-- **Assumptions:** There is no difference in distribution between any facet or x-category -->
<!-- nsim = 200 -->
<!-- lambda = 0.67 -->

@@

Figure \ref{fig:normal-3diff} shows distribution of wpd for N(0,1), N(5,1) and N(0,5) distribution to see the effect of changing location and scale on the distribution of wpd. It seems like the  distribution changes across different facet and x levels but look same for different  normal distributions, which implies wpd value is unaffected by the change is location and scale of the the normal distribution.

@@

### Gamma Distribution

@@

@@

## Choice of tuning parameters and effect of different increments

Objective: Choice of optimal tuning parameter $lambda$ with the help of two alternate designs (vary_x and vary_f)  for different nx and nfacets. The lambda for which the two designs intersect have to be chosen to put appropriate weights for within-facet and between-facet distances.

@@

```{r tuning-one-omega, fig.caption = "WPD from two designs are plotted for different values of lambda for different x and facet categories. For omega = 1, the designs intersect for 0.6<lamba<=0.75, whereas for higher omega, design intersects at lambda = 0.5", eval = FALSE}
knitr::include_graphics(here::here("simulations/tuning_param/figs/fixed_omega.png"))
```

How value of lambda changes with increasing omega

```{r tuning-parameter-intersection, eval = FALSE}
knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
```

@@

## Alternate designs

>>>>

## Distribution of wpd

### $D_{null}$

**Objective:**  Study the behavior of wpd under different initial distributions for different $nx$ and $nfacet$

@@

wpd is computed for different normal and non-normal distributions to see how the underlying distribution has a role to play in the value of wpd. Since we are concerned with detecting the differences in distributions, it would be ideal if wpd has minimal dependency on the type, location and scale of the  underlying distribution. To that end, some pre-processing of the data is preferred to bring it to the same scale, location and type.
The Normal Score Transform or NQT has been applied in various fields of geo-statistics in order to make most asymmetrical distributed real world measured variables more
treatable and normal-like.

@@

<!-- **Assumptions:** There is no difference in distribution between any facet or x-category -->
<!-- nsim = 200 -->
<!-- lambda = 0.67 -->

@@

Figure \ref{fig:normal-3diff} shows distribution of wpd for N(0,1), N(5,1) and N(0,5) distribution to see the effect of changing location and scale on the distribution of wpd. It seems like the  distribution changes across different facet and x levels but look same for different  normal distributions, which implies wpd value is unaffected by the change in location and scale of the the normal distribution.

Figure \ref{fig:mean-sd-ns-nfacet} shows how mean and sd of the distribution of wpd changes with the increasing x and facet levels. It seems like both mean and standard deviation are affected more by change in the x-axis levels than the facet levels.

@@

@@

```{r gamma-diff-trans, fig.cap="Ridge plots of raw wpd is shown for G(0.5,1) and G(2,1) distribution after quantile transformation looks similar and hence is unaffected by change in location.", fig.pos="h"}
knitr::include_graphics(here::here("simulations/raw/null_design_quantrans/figs/diff_mean3_gamma.png"))
```

@@

### Alternate designs

Objective: Study the effect of different tuning parameters $\lambda$ and $\omega$     with the help of two alternate designs ($vary_x$ and $vary_f$) for different $nx$ and $nfacet$. The $\lambda$ for which the two designs intersect will then be chosen as the optimal $\lambda$ that could then be weighed appropriately to up-weigh the within-facet distances and down-weigh the between-facet distances. Figure \ref{fig:tuning-one-omega} are plotted for different values of $\lambda$ for a relatively small and higher $\omega$. Designs mostly intersect at $\lambda = 0.5$ for the higher value of $\lambda$. Figure \ref{fig:tuning-parameter-intersection} shows how the value of lambda changes with increasing omega.

@@

```{r tuning-one-omega, fig.caption = "WPD from two designs are plotted for different values of lambda for different x and facet categories. For omega = 1, the designs intersect for 0.6<lamba<=0.75, whereas for higher omega, design intersects at lambda = 0.5"}
knitr::include_graphics(here::here("simulations/tuning_param/figs/fixed_omega.png"))
```

```{r tuning-parameter-intersection, fig.cap="For most panels it is observed that the most common values for which the "}
knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
```

@@
